---
title: "Transmittal Notice"
output: pdf_document
date: "`r format(as.Date(Sys.Date()), '%B %d, %Y')`"
header-includes: 
  - \usepackage{wrapfig}
  - \usepackage{graphicx}
---

\fontsize{14pt}{16pt}\selectfont

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dpi = 300) 
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
library(BarnebyLives)
```

```{r user defined settings}
herbarium_code <- 'US'
project <- data.frame(
  Name = 'Seeds of Success',
  Organization = 'Chicago Botanic Garden',
  Person = 'Reed Clark Benkendorf',
  Email = 'rbenkendorf@chicagotbotanic.org',
  Phone = '1-815-255-0631',
  PersonTitle = 'Senior (field) Botanist'
)
```

```{r load data}
herbarium <- herbaria_info |> 
  dplyr::filter(Abbreviation == herbarium_code)

p <- '../results/'
f <- paste0(p, list.files(p)[ grep('-', list.files(p)) ]) 

specimens = data.table::rbindlist(lapply(f, data.table::fread), fill = T) |> 
  dplyr::select(Primary_Collector, Collection_number, Full_name) |> 
  dplyr::filter(! Collection_number %in% c(370, 371)) |>
  dplyr::mutate(
    Packed = "", 
    Received = "", 
    Primary_Collector = stringr::str_replace(Primary_Collector, "[a-z]+", "."),
    Primary_Collector = stringr::str_replace(Primary_Collector, "Clark", "C.")) 
```

`r herbarium$Contact`  
`r herbarium$Name1`  
`r herbarium$Name2`  
`r herbarium$Street`   
`r herbarium$City`, `r herbarium$State`

\vspace{1cm} 

Dear `r herbarium$Contact`,

\vspace{0.5cm} 

We at `r project$Organization` are transferring these materials to `r herbarium$Abbreviation` to serve as vouchers for the `r project$Name` native seed conservation and development project. 

\vspace{0.5cm} 

This package contains the specimens noted on the following page, and labels for them enclosed in the sheets. The material in here is intended to represent a single set from collections made in quadruplicate. These materials were collected under the auspices of the US Department of Interiors Bureau of Land Management, unless noted otherwise.

\vspace{0.5cm} 

If you are interested, we are able to share digital copies of relevant collection data to assist digitization endeavors.

\vspace{0.5cm} 

Thank you, we appreciate both your and your staffs assistance in this matter. Please do not hesitate to reach out to me with any questions. 

\vspace{1cm} 

\begin{wrapfigure}{r}{0.15\textwidth}
  \centering
    \includegraphics[width=0.15\textwidth]{CBG-logo.png}
\end{wrapfigure}

Sincerely,

\vspace{0.5cm} 
\fontsize{14pt}{14pt}\selectfont

`r project$Person`  
`r project$PersonTitle`   
`r project$Phone`   
`r project$Email`   

\newpage

```{r Specimen table}
knitr::kable(specimens, longtable = TRUE, booktabs = FALSE,  
             col.names = c('Collector', '#', 'Taxon', 'Pack.', 'Rec.')) |>
  kableExtra::column_spec(3, '10em') |>
  kableExtra::kable_styling(latex_options = c( "repeat_header")) 
```

```{r clean environment}
rm(herbarium_code, project_code, herbarium, project, specimens)
```


