---
title: "stack and subset WNA predictors"
author: "Reed"
date: "2023"
output:
  pdf_document: default
---

We are going to test out Ian Breckheimers 32 Predictor Raster Brick. It covers from roughly the Black Hills West. Apologies West Texas & Sidney Montana. 

```{r, message = F, warning = F}
library(sf)
library(tidyverse)
library(terra)
library(spData)
source('functions.R')
```


# Option 1. Utilizing the Western Colorado .tif as a centerpiece to the area of analysis. 

the Southern Rockies tiles are already put together here

```{r}
p <- '../../geodata'
f <- list.files(p, recursive = T, pattern = 'shp$')

field_off <- st_read(file.path(p, f[grep('GRT', f)]), quiet = T) %>% 
  st_union() %>% 
  st_as_sf() %>% 
  st_transform(5070)

field_off <- nngeo::st_remove_holes(field_off)
field_off <- st_buffer(field_off, dist = 50000)
field_off <- st_convex_hull(field_off)

gr <- st_make_grid(field_off, n = c(6,6)) %>% 
  st_as_sf() %>% 
  mutate(QUADRAT = paste0(rep(LETTERS[1:6], each = 6), rep(1:6, 6))) %>% 
  st_intersection(field_off, .)
  
```

we can add more tiles to increase the area of analysis. 
```{r}

path <- "/hdd/Geospatial_data/Western_Plant_Predictors/SDM_tiles_WNA"
tile_index <- list.files(path, pattern = ".shp$")
path <- paste0(path, "/")
index <- sf::st_read(paste0(path, tile_index), quiet = T) %>% 
  mutate(tiles = str_extract(location, "\\d+")) %>% 
  mutate(tiles = as.numeric(as.character(tiles))) %>% 
  st_transform(5070) %>% 
  mutate(location = str_replace(location, "/Users/ian/GIS/SDM_tiles_WNA/", path))

box <- st_bbox(st_buffer(index, 1000000))
us_states <- st_transform(us_states ,5070)
us_states <- st_crop(us_states, box)

#png(filename = 'C:/R_datsci_2022/Spatial_lecture_developement/pictures/Western_Plant_Predictors.png', width = 1080, height = 720, units = "px", pointsize = 16)
ggplot()+
  geom_sf(data = us_states) +
  geom_sf(data = field_off, fill = 'black') +
  geom_sf(data = index, aes(fill = tiles), alpha = 0.6) +
  viridis::scale_fill_viridis() +
  theme_bw() +
  labs(title = 'Western Plant Predictors 32-layer Stack', fill = 'Tile Number') +
  theme(plot.title = element_text(hjust = 0.5), 
        text = element_text(size=20))

rm(path, tile_index, us_states)
```

Determine which tiles are required for each quadrat 
```{r}

index <- st_intersection(gr, index) # clip tiles to ecoregion
index1 <- as.data.frame(st_covered_by(index, field_off))

index <- index %>% mutate(row.num = row_number())
index <- index %>% 
  filter(!row.num %in% index1)

# field_off <- as(field_off, "Spatial")

rm(ecoregions, ecoregion_bound, buffer_distance,  index1)
```

# Match up the spatial extents of the existing raster and that which we are making.

We need to re-project the rasters before stacking. 
```{r, eval = F}
files <- index %>% pull(location)
newproj <- "epsg:5072" 
ppred <- '/hdd/Geospatial_data/Western_Plant_Predictors/'

ifelse(!dir.exists(file.path(ppred, 'GreatBasin')), 
       dir.create(file.path(ppred, 'GreatBasin')), FALSE)

splindex <- split(index, index$QUADRAT)
inner_bounds <- vect(gr) |> project(newproj)
outer_bounds <- vect(field_off) |> project(newproj)

lapply(splindex, FUN = import_crop, y = inner_bounds, ppred = '/hdd/Geospatial_data/Western_Plant_Predictors/')

rm(files.list, wppr, allrasters, files, index, splindex)
```


```{r}
rasty <- file.path(ppred, 'GreatBasin',
  list.files(file.path(ppred, 'GreatBasin'))
)

collection <- vrt(rasty)
```

